---
title: "user"
author: user
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume', 'https://cdn.rawgit.com/jpswalsh/academicons/master/css/academicons.min.css']
    self_contained: true
---

```{r, include=FALSE, cache = F}
knitr::opts_chunk$set(
  results='asis',
  echo = FALSE
)

library(glue)
library(tidyverse)


# Holds all the links that were inserted for placement at the end
PDF_EXPORT <- FALSE

source('R/parsing_functions.R')

# Load csv with position info
position_data <- readr::read_csv('data/positions.csv')
```

 
Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------
- <i class="fa fa-github"></i> [user](https://github.com/user)
- <i class="fa-brands fa-linkedin"></i> [LinkedIn](https://www.linkedin.com/in/mon-nom-2504321b0/)
- <i class="fa fa-envelope"></i> <a href="mailto:test@icloud.com">Courriel</a>



Compétences techniques
------------------------------------
<span style="font-weight:600;">Base de données</span>:
<span style="font-weight:600;">analyses</span>: <br> Statistique bayesienne (Stan), modèles hiérarchiques <br>



------------------------------------

 <br>SQL - Postgres<br>

<span style="font-weight:600;">Automation/reports</span>: <br>Git, Markdown, LaTeX<br> 


Languages
------------------------------------
**Français**<span style="font-size:11px;"> Langue maternelle</span><br>
**Anglais**<span style="font-size:11px;"> Niveau B2</span><br>


Main
================================================================================

 <span style="font-weight:600">Mon nom</span> <span style="font-size: 13px;">M.Sc.</span>{#title}
--------------------------------------------------------------------------------

 
<span style="font-size: 1rem;">< <i class="fa fa-bar-chart"></i> + <i class="fa fa-laptop"></i> > Bioinformaticien </span>

Expériences professionnelles {data-icon=laptop}
--------------------------------------------------------------------------------
```{r}
print_section(position_data, 'work')
```

Diplômes {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------
```{r}
print_section(position_data, 'education')
```

Enseignements {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------
```{r}
print_section(position_data, 'teach')
```

Bénévolat {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------
```{r}
print_section(position_data, 'volunteering')
```

Publications {data-icon=book}
--------------------------------------------------------------------------------

### Graph embedding and transfer learning can help predict potential species interaction networks despite data limitations

Methods in Ecology and Evolution - <a href=" https://doi.org/10.1111/2041-210X.14228"><i class="ai ai-doi"></i></a>

N/A

2023

- <span style="color:#000000 !important;">T Strydom, S Bouskila, F Banville, C Barros, D Caron, M J.Farrell, MJ Fortin, B Mercier, L J.Pollock, R Runghen, G V.Dalla Riva, T Poisot</span>

### Food web reconstruction through phylogenetic transfer of low-rank network representation

Methods in Ecology and Evolution - <a href="https://doi.org/10.1111/2041-210X.13835"><i class="ai ai-doi"></i></a>

N/A

2022

- <span style="color:#000000 !important;">T Strydom, S ouskila, F Banville, C Barros, D Caron, M J.Farrell, MJ Fortin, V Hemming, B Mercier, L J.Pollock, R Runghen, G V.Dalla Riva, T poisot</span>

### A roadmap towards predicting species interaction networks (across space and time)

Philosophical Transactions of the Royal Society B <a href="https://doi.org/10.1098/rstb.2021.0063"><i class="ai ai-doi"></i></a>

N/A

2021

- <span style="color:#000000 !important;">T Strydom, MD Catchen, F Banville, D Caron, G Dansereau, P Desjardins-Proulx, NR Forero-Muñoz, G Higino, B Mercier, A Gonzalez, D Gravel, L Pollock, T Poisot</span>

### Global knowledge gaps in species interaction networks data

Journal of Biogeography <a href="https://doi.org/10.1111/jbi.14127"><i class="ai ai-doi"></i></a>

N/A

2021

- <span style="color:#000000 !important;">T Poisot, G Bergeron, K Cazelles, T Dallas, D Gravel, A Macdonald, B Mercier, C Violet, S Vissault.</span>

### R package - [rmangal](https://docs.ropensci.org/rmangal/)

N/A

N/A

2019

- <span style="color:#000000 !important;">Vissault S, Cazelles K, Bergeron G, Mercier B, Violet C, Gravel D,
Poisot T (2019). _rmangal: An R package to interact with Mangal
database_. R package version 2.0.0.</span>
